### 2024-07-18 conteudo/background/codeduplication.tex
Add small missing things in background

\subsection{Methodology to evaluate code duplication methods}

@@

Given the necessity to evaluate and compare approches for code clone detection, it was developed and widely-adopted two datasets: 
OJ-Clone, a dataset collected from a pedagogical online judge system \citep{ojclone}, and BigCloneBench, a dataset collected from over 
25,000 Java software systems \citep{bigclonebench}. The existence of only two spreaded datasets is a open concern in literature as 
the limited scope of OJ-Clone and the problems of BigCloneBench presented by Krinke and Ragkhitwetsagul \citep{bigfail}

(ADD INFORMATION ABOUT THE MORE SEPARATION OF CLONE TYPES THE BIGCLONEBENCH makes)

>>>>

\subsection{Evaluating code duplication methods}

@@

Given the necessity to evaluate and compare approaches for code clone detection, it was developed and widely 
adopted: OJ-Clone, a dataset collected from a pedagogical online judge system \citep{ojclone},
and BigCloneBench, a dataset collected from over 25,000 Java software systems \citep{bigclonebench}. 
The existence of only two spread datasets is an open concern in literature as the limited scope of OJ-Clone 
and the problems of BigCloneBench presented by Krinke and Ragkhitwetsagul \citep{bigfail}. The BigCloneBench
is the dataset used by most of the literature works, given the limited pedagogical scope of the OJ-Clone.

To evaluate the code clone detection approaches against the datasets, the works compute metrics using 
the predictions made related to the instances of the dataset. There are four possible outcomes when an 
instance is predicted by a code clone detection approach, which are:

\begin{itemize}
	\begin{item}
		\textit{True positivity (TP)}: This outcome happens when the approach predicts that the instance 
		is a code clone and the instance is a code clone.
	\end{item}
	\begin{item}
		\textit{False positivity (FP)}: This outcome happens when the approach predicts that the instance 
		is a code clone, but the instance is not a code clone.
	\end{item}
		\begin{item}
		\textit{True negative (TN)}: This outcome happens when the approach predicts that the instance 
		is not a code clone and the instance is not a code clone.
	\end{item}
	\begin{item}
		\textit{False negative (FN)}: This outcome happens when the approach predicts that the instance 
		is not a code clone, but the instance is a code clone.
	\end{item}
\end{itemize}

Given the number of TP, FP, TN, and FN that resulted after an approach evaluation against a dataset,
it is possible to compute classical metrics such as Precision, Recall, and F-Score \citep{recall}.
In this work, we use the Recall metric as the code clone detection approaches usually make available 
this metric to compare themselves in contrast with the others. The Recall metric is defined by the 
following formula \citep{recall}:

$$Recall = \frac{\sum TP}{\sum TP + \sum FN }$$

Where $\sum TP$ is the number of true positives in the evaluation and $\sum FN$ is the number of 
false negatives. The Recall metric is a number between $0$ and $1$, where a value closer to $1$ is 
better, and a value closer to $0$ is worse.

### 2024-07-18 conteudo/background/linux.tex
Add small missing things in background

One of the Linux kernel subsystems is the AMD Display Driver, a subsystem responsible for 
implementing the drivers required to enable AMD GPU to work properly in the Linux environment. 
The maintainers of this subsystem reported an empirical problem they have in the subsystem, which is 
a significant amount of duplicated code in the subsystem, which hinders the maintenance of the subsystem.
This reported problem is the starting point that initiated our research, making the AMD Display Driver our 
principal object of study to understand how to mitigate duplicated code in the Linux kernel.

>>>>

One of the Linux kernel subsystems is the AMD Display Driver, a subsystem responsible for implementing 
the drivers required to enable AMD GPU to work correctly in the Linux environment. The maintainers of 
this subsystem reported an empirical problem they have in the subsystem, which is a significant amount 
of duplicated code in the subsystem, which hinders the maintenance of the subsystem. The reported issue 
is the starting point that initiated our research, making the AMD Display Driver our principal object 
of study to understand how to mitigate duplicated code in the Linux kernel. The AMD Display Driver 
contains X code lines, Y functions/structs, and Z code files, representing a significant amount of 
the Linux kernel. As with any other Linux subsystem, the discussions related to the AMD Display Driver 
are made in its proper mailing list (FIND MAILING LIST AND CITE HERE).
